Dynamic Modeling for Optimal Cryptoeconomic Policies

### 2023-10-13 Presentations/lightning_slides.tex
new pitch slides

\title[Optimal Cryptoeconomic Policies]{Dynamic Modeling for Optimal Cryptoeconomic Policies}
\subtitle{Pitch Proposal 2}
\author{Mingxuan He}

@@

\textbf{How should we design dynamic staking and burning policies?}\newline
\begin{itemize}
\item Current protocol-coded policies are static even though crypto-economies face dynamic shocks. ``Staking" and ``burning" rates are the primary coded policy rules in the underlying blockchain system
\begin{itemize}
    \item \textbf{Staking (increases ``token supply", decreases ``tokens in circulation")}: mint new tokens and give to those who stake their existing tokens as interest. Similar to interest on reserves.
    \item \textbf{Burning (decreases ``token supply")}: burn (remove from circulation) a portion of the transaction fee paid by users during blockchain transactions
    \end{itemize} \textbf{}

@@

        \item Pricing models of cryptocurrencies:\\
        {\footnotesize Bitcoin: \textit{\citet{athey2016bitcoin, garratt2018bitcoin, schilling2019some, schilling2019currency, catalini2020some, biais2020equilibrium, bolt2020value, hinzen2022bitcoin, chiu2017economics}, etc.}}\\
        {\footnotesize Proof-of-stake: \textit{\citet{catalini2020markets, saleh2019volatility, saleh2021blockchain}}}\\
        $\rightarrow$ \textbf{Static token supply means all shocks are absorbed by price}
        \item Monetary policies for stablecoins, platform tokens, and CBDCs:\\
        {\footnotesize \textit{\citet{cong2021tokenomics, cong2022token, d2022can, fernandez2021central, zhu2019framework, sockin2023model, sockin2023decentralization}, etc.}}\\
        $\rightarrow$ \textbf{Optimizing policy for defending peg and/or making profit}
    \end{itemize}
\end{frame}

@@

%----------------
\section{Model (baseline)}
\begin{frame}{The baseline model (Biais et al. 2020, Journal of Finance)}
\textbf{Idea:} The fundamental value of crypto comes from the stream of future transactional benefits \parencite{tirole1985asset}\\
\begin{itemize}
    \item e.g. access to unique goods, not expropriated/taxed/constrained by government, direct internet access
\end{itemize}
\textbf{Setup:} Two-period model with overlapping generations
\begin{itemize}
    \item Three actors: users, validators (miners), hackers
    \item Three financial assets: a risk-free asset, a standard currency (dollar), a cryptocurrency (Bitcoin)
    \item Sources of shocks: endowment, transactional benefit, fees
\end{itemize}
\textbf{Result:} Bitcoin price changes partly due to changes in net transactional benefits, but mostly extrinsic volatility
\end{frame}

\begin{frame}{The baseline model (Biais et al. 2020, Journal of Finance)}
\[
\begin{tikzcd}[ampersand replacement=\&, column sep = 4.5em, row sep = 4.5em]
Protocol 
\ar[d, "\substack{\text{newly minted}\\\text{tokens}}" ']
\&
\ar[d, shift right, "\substack{\text{endow-}\\ \text{ment}}" 'near start]
\ar[d, shift left, "\substack{\text{purchase}\\ \text{assets}}" near start]
\&
\ar[d, "\substack{\text{transact.}\\ \text{benefits}}" ]
\&
\\
Validators
\& 
\substack{Young\\Users}
\ar[l,"\substack{\text{transact.}\\ \text{fees}}" ']
\ar[r, dashed, "t+1", 
"\substack{\text{hold}\\\text{assets}}" ']
\& 
\substack{Old\\Users}
\ar[r, "\substack{\text{hacked}\\ \text{tokens}}"]
\&
Hackers
\end{tikzcd}
\]
In each period: %\hyperlink{formal}{\beamerbutton{Formal Problem}}
\begin{itemize}
    \item \textbf{Young users} receive endowment, spend on consumption goods \& financial assets. Pay fees on crypto purchased
    \item \textbf{Old users} consume savings (some crypto savings get hacked), and receive transactional benefits
    \item \textbf{Validators} receive newly minted tokens as block rewards
    \item \textbf{Hackers} hack a portion of users' crypto
\end{itemize}
\end{frame}

\begin{frame}{The baseline model: Users}
\label{formal}
\begin{align}
    \text{Young users: } c_t^y &= e_t- s_t - (1+\varphi_t) q_t p_t - \hat{q}_t \hat{p}_t\\
    \text{Old users: } c_{t+1}^o &= s_t (1+r_t) + (1-h_{t+1}) q_t p_{t+1} + \hat{q}_t \hat{p}_{t+1} \nonumber \\
    &+ \theta_{t+1} (1-h_{t+1}) q_t p_{t+1} 
\end{align}

$e_t$: endowment\\
$s_t$: quantity of risk-free assets held\\
$q_t, \hat{q}_t$: quantities of crypto and dollars held\\
$p_t, \hat{p}_t$: prices (in units of consumption goods) of crypto and dollars\\
$h_{t+1}$: portion of crypto hacked by hackers\\
$\varphi_t$: transaction fees involved in using crypto (exog.)\footnote{The analysis remain largely unchanged if we include a transaction cost when selling crypto in period $t+1$ as well.}\\
$\theta_{t+1}$: transactional benefits from using crypto (exog.) (assume $\theta_{t+1}\geq-1$) \\

@@

\begin{frame}{The baseline model: Validators and hackers}
\begin{align}
    \text{Validators: } c_{t+1}^v &= (X_{t+1} - X_t) p_{t+1} + \varphi_{t+1} q_{t+1} p_{t+1}\\
    \text{Hackers: } c_{t+1}^h &= h_{t+1} q_t p_{t+1}
\end{align}
$X_t$: stock token supply\\
$X_{t+1} - X_t$: increase in token supply (newly minted tokens)
\end{frame}

\begin{frame}{The baseline model: Market clearing}
Markets for financial assets:
\begin{align}
    \text{crypto: } q_t &= X_t \\
    \text{dollars: } \hat{q}_t &= m \\
    \text{risk-free assets: } s_t &= 0 \\
\end{align}
Market for consumption goods (by Walras's Law):
\begin{equation}
    c_t^y + c_t^o + c_t^v + c_t^h = e_t
\end{equation}

@@

\begin{frame}{The baseline model: Solution}
A young user in period $t$ solves:
\begin{align}
\max_{s_t, q_t, \hat{q}_t} &u(c_t^y) + \beta\mathbb{E}_t u(c_{t+1}^o)\\  
    \text{subject to  } & \text{user's budget constraint} \nonumber
\end{align}
$^*$ Information set at period $t$ includes $ \{\theta_t, \varphi_t, \pi_t\}$ \\
From FOCs obtain the equilibrium pricing equation for crypto:
\newcommand{\vp}{\vphantom{\frac{u'(c_{t+1}^o)}{\mathbb{E}_t[u'(c_{t+1}^o)]}}}
\begin{equation}
    p_t = 
    \underbrace{\vp
    \frac{1}{1+r_t}}_\text{discount}
    \mathbb{E}_t \Bigl[ 
    \underbrace{\frac{u'(c_{t+1}^o)}{\mathbb{E}_t[u'(c_{t+1}^o)]}} _\text{risk-neutral prob}
    \underbrace{\vp
    (1-h_{t+1})} _\text{hack risk}
    \underbrace{\vp
    \frac{1+\theta_{t+1}}{1+\varphi_t}} _{\substack{\text{net transact.}\\ \text{benefits}}}
     p_{t+1}
    \Bigr]
\end{equation}    
\end{frame}

%----------------------------------
\section{Model (extended)}
\begin{frame}{Extension 1: Endogenous token supply}
\[
\begin{tikzcd}[ampersand replacement=\&, column sep = 4.5em, row sep = 4.5em]
Protocol 
\ar[d, shift right, "\substack{\text{newly minted}\\\text{tokens}\\(t+1)}" ']
\&
\ar[d, shift right, "\substack{\text{endow-}\\\text{ment}}" 'near start]
\ar[d, shift left, "\substack{\text{purchase}\\ \text{assets}}" near start]
\&
\ar[d, "\substack{\text{transact.}\\ \text{benefits}}" ]
\&
\\
Validators
\ar[u, shift right, red, "\substack{\text{stake}\\\text{tokens}\\(t)}" ' red ]
\& 
\substack{Young\\Users}
\ar[l,"\substack{\text{variable}\\ \text{fees (``tip")}}" ']
\ar[lu, red, "\substack{\text{base fees}\\ \text{(burned)}}" {sloped,auto}' red]
\ar[r, dashed, "t+1", 
"\substack{\text{hold}\\\text{assets}}" ']
\& 
\substack{Old\\Users}
\ar[r, "\substack{\text{hacked}\\ \text{tokens}}"]
\&
Hackers
\end{tikzcd}
\]
I introduce:
\begin{itemize}
    \item Two-part transaction fee with burning
    \item Interest-bearing staking
    \item The protocol controls the staking yield (``interest rate") and the base transaction fee rate (burn rate)
\end{itemize}
\end{frame}

\begin{frame}{Introducing staking and burning}
$^*$ The following is work in progress\\

\textbf{Staking:}
$L_t$: amount of staked tokens; $\delta_t$: staking yield (set by protocol)\\
\textbf{Burning:}
$\varphi_t^b$: base fee (set by protocol); $\varphi_t^v$: variable fee (competitively determined by validators and users)\\
\ \\
\textbf{New budget constraints:}
\begin{align}
    \text{Young users: } c_t^y &= e_t - s_t - (1+{\color{red} \varphi_t^b+\varphi_t^v}) q_t p_t - \hat{q}_t \hat{p}_t\\
    \text{Old users: } c_{t+1}^o &=  s_t (1+r_t) + (1-h_{t+1}) q_t p_{t+1} + \hat{q}_t \hat{p}_{t+1} \nonumber \\
     &\hspace{2em} + \theta_{t+1} (1-h_{t+1}) q_t p_{t+1}\\ 
    \text{Validators: } c_{t+1}^v &= {\color{red} (1+\delta_t) L_t} p_{t+1} + {\color{red} \varphi_{t+1}^v} q_{t+1} p_{t+1} {\color{red} - L_{t+1} p_{t+1} }\\
    \text{Hackers: } c_{t+1}^h &= h_{t+1} q_t p_{t+1}
\end{align}
\end{frame}

\begin{frame}{Token supply with staking and burning}
\begin{align}
    M_{t+1} &= (M_t - L_t) + L_t (1 + \delta_t) - \varphi_t^b X_t \nonumber \\
    &= M_t + \delta_t L_t - \varphi_t^b X_t
\end{align}
$M_t$: total token supply\\
$X_t \equiv M_t - L_t$: circulating supply \\
\quad $\Rightarrow$ Now market clearing condition is $X_t=q_t$\\
\ \\
$^*$ In reality the total reward is $\delta_t L_t^\alpha$, with pre-set $\alpha\in [0,1]$\footnote{$\alpha=0.5$ for Ethereum. See Ethereum Documentation. ``Proof-of-Stake Rewards and Penalties"}. Here I set $\alpha=1$ WLOG since $\delta_t$ is dynamic.
% calculations: https://blog.bitmex.com/ethereums-proof-of-stake-system-calculating-penalties-rewards/
\end{frame}

\begin{frame}{Validator's problem}
% should validators pay transaction fees when they cash out?
\begin{align}
\max_{L_{t+1}}\ & u((1+\delta_t) L_t p_{t+1} + \varphi_{t+1}^v q_{t+1} p_{t+1} - L_{t+1}p_{t+1})\\
    \text{s.t. } & q_{t+1} \leq M_{t+1} - L_{t+1} \nonumber
\end{align}
\textbf{Trade-off:}
\[
\text{more staking at } t \Rightarrow
\begin{cases}
    \text{more staking yield at } t+1\\
    \text{less circulating supply} \Rightarrow \text{less transact. fees at } t
\end{cases}
\]
Apply Karush-Kuhn-Tucker to solve the optimization problem
\end{frame}

%----------------
\section{Next Steps}
\begin{frame}{Next Steps}
    \begin{itemize}
        \item \textbf{The model:} Finish extended model with staking and burning, obtain analytical solution for equilibrium pricing, run simulations using dynare / Python\\
        \item \textbf{Replicate calibration:} Replicate calibration for baseline model (authors provided full replication code in Python)
        \item \textbf{Get data on Ethereum:} 
        \begin{itemize}
            \item ETH price data: Messari API\footnote{https://messari.io/api} (REST) and Dune Analytics\footnote{https://dune.com/docs/api} (SQL database with execution API in Python)
            \item ETH staking and burning data: Beacon Chain\footnote{https://ethereum.github.io/beacon-APIs} (REST)
        \end{itemize}
        \item \textbf{Calibrate my model}: get ideas after replicating calibration
    \end{itemize}
\end{frame}

@@

% -----------------
\section*{}
\begin{frame}[allowframebreaks]{References}
    \nocite{*}
    %\bibliographystyle{apalike}
    %\bibliography{references}
    \printbibliography
\end{frame}

>>>>

\title[Optimal Cryptoeconomic Policies]{Dynamic Modeling for Optimal Cryptoeconomic Policies}
\subtitle{Pitch Proposal Fall 2023}
\author{Mingxuan He}

@@

\textbf{How should we design dynamic staking and burning policies for Proof-of-Stake cryptoeconomies?}\newline
\begin{itemize}
\item Current protocol-coded policies are static even though crypto-economies face dynamic shocks. ``Staking" and ``burning" rates are the primary coded policy rules in the underlying blockchain system
\begin{itemize}
    \item \textbf{Staking (increases ``token supply", decreases ``tokens in circulation")}: mint new tokens and give to those who stake their existing tokens as interest. Similar to interest on reserves.
    \item \textbf{Burning (decreases ``token supply")}: burn (remove from circulation) a portion of the transaction fee paid by users during blockchain transactions
    \end{itemize} \textbf{}

@@

        \item Pricing models of cryptocurrencies:\\
        {\footnotesize Bitcoin: \textit{\citet{athey2016bitcoin, garratt2018bitcoin, schilling2019some, schilling2019currency, catalini2020some, biais2023equilibrium, bolt2020value, hinzen2022bitcoin, chiu2017economics}, etc.}}\\
        {\footnotesize Proof-of-stake: \textit{\citet{catalini2020markets, saleh2019volatility, saleh2021blockchain}}}\\
        $\rightarrow$ \textbf{Static token supply means all shocks are absorbed by price}
        \item Monetary policies for stablecoins, platform tokens, and CBDCs:\\
        {\footnotesize \textit{\citet{cong2021tokenomics, cong2022token, cong2022staking, d2022can, fernandez2021central, zhu2019framework, sockin2023model, sockin2023decentralization}, etc.}}\\
        $\rightarrow$ \textbf{Optimizing policy for defending peg and/or making profit}
    \end{itemize}
\end{frame}

@@

%----------------
\section{Model}
% \begin{frame}{Inspiration}
%     \begin{figure}
%         \includegraphics[width=0.75\textwidth]{biais_title.png}
%     \end{figure}
%     * Bitcoin's economic/consensus system (proof-of-work) is different from proof-of-stake
% \end{frame}

\begin{frame}{A model of proof-of-stake cryptoeconomies}
    \[
\begin{tikzcd}[ampersand replacement=\&, column sep = 4.5em, row sep = 4.5em]
Protocol 
\ar[d, shift right, "\substack{\text{newly minted}\\\text{tokens}\\(t+1)}" ']
\&
\ar[d, shift right, "\substack{\text{endow-}\\\text{ment}}" 'near start]
\ar[d, shift left, "\substack{\text{purchase}\\ \text{assets}}" near start]
\&
\ar[d, "\substack{\text{transact.}\\ \text{benefits}}" ]
\&
\\
Validators
\ar[u, shift right, red, "\substack{\text{stake}\\\text{tokens}\\(t)}" ' red ]
\& 
\substack{Young\\Users}
\ar[l,"\substack{\text{variable}\\ \text{fees (``tip")}}" ']
\ar[lu, red, "\substack{\text{base fees}\\ \text{(burned)}}" {sloped,auto}' red]
\ar[r, dashed, "t+1", 
"\substack{\text{hold}\\\text{assets}}" ']
\& 
\substack{Old\\Users}
\ar[r, "\substack{\text{hacked}\\ \text{tokens}}"]
\&
Hackers
\end{tikzcd}
\]

\begin{itemize}
    \item Inspired by Biais et al. (J Finance 2023) ``Equilibrium Bitcoin Pricing"
    \item Two-period OLG model
    \item Endogenous token supply (innovation over \citet{biais2023equilibrium})
    \item Assumption: Crypto's fundamental value comes from the stream of future transactional benefits\\
    \begin{itemize}
        \item e.g. access to unique goods, not expropriated/taxed/constrained by government, direct internet access
    \end{itemize}
\end{itemize}

@@

\begin{frame}{User's problem}
    \begin{itemize}
    \item Period t: allocates endowment income $e_t^u$ into three asset classes: risk-free $s_t$, crypto $q_t$, and fiat $\hat{q}_t$. To buy crypto they pay a two-part transaction fee $\varphi_t^b$ (burned) and $\varphi_t^v$ (goes to validator)\\
    \item Period t+1: receive interest $r_t$, transactional benefits $\theta_{t+1}$, and hacking loss $h_{t+1}$\\
    \end{itemize}

    \begin{align}
    c_t^u &= e_t^u - s_t - (1+ \varphi_t^b+\varphi_t^v) q_t p_t - \hat{q}_t \hat{p}_t\\
    c_{t+1}^u &=  s_t (1+r_t) + (1-h_{t+1})(1+\theta_{t+1}) q_t p_{t+1} + \hat{q}_t \hat{p}_{t+1}
    \end{align}

@@

\begin{frame}{Validator's problem}
    \begin{itemize}
        \item Period t: receive transaction fees $\varphi_t^v$, stake $L_t$
        \item Period t+1: receive staking yield $\delta_t$
    \end{itemize}
    \textbf{Trade-off:}
    \[
    \text{more staking at } t \Rightarrow
    \begin{cases}
        \text{more staking yield at } t+1\\
        \text{less circulating supply} \Rightarrow \text{less transact. fees at } t
    \end{cases}
    \]
    \begin{align}
    c_t^v &= e_t^v + \varphi_t^v q_t p_t - L_t p_t \\
    c_{t+1}^v &= (1+\delta_t) L_t p_{t+1} 
    \end{align}
\end{frame}

\begin{frame}{Token supply}
    \begin{align}
        M_{t+1} &= (M_t - L_t) + L_t (1 + \delta_t) - \varphi_t^b X_t \nonumber \\
        &= M_t + \delta_t L_t - \varphi_t^b X_t
    \end{align}
    $M_t$: total token supply\\
    $X_t \equiv M_t - L_t$: circulating supply \\
    \quad $\Rightarrow$ Token market clearing condition is $X_t=q_t$\\
    \ \\
    $^*$ In reality the total reward is $\delta_t L_t^\alpha$, with pre-set $\alpha\in [0,1]$\footnote{$\alpha=0.5$ for Ethereum. See Ethereum Documentation. ``Proof-of-Stake Rewards and Penalties"}. Here I set $\alpha=1$ WLOG since $\delta_t$ is dynamic.
    % calculations: https://blog.bitmex.com/ethereums-proof-of-stake-system-calculating-penalties-rewards/
\end{frame}

\begin{frame}{First order conditions}
    * for a deterministic version of the model
    \bigskip

    User's Euler equations:
    \begin{equation}
        \frac{u'(c_t^u)}{u'(c_{t+1}^u)} = \beta (1+r_t) 
        = \beta \frac{(1+\theta_{t+1})(1-h_{t+1})}{1+\varphi_t^b+\varphi_t^v} \frac{p_{t+1}}{p_t}
        = \beta \frac{\hat{p}_{t+1}}{\hat{p}_t}
    \end{equation}

    Validator's Euler equation:
    \begin{equation}
        \frac{u'(c_t^v)}{u'(c_{t+1}^v)} = \beta (1+\delta_t) \frac{p_{t+1}}{p_t}
    \end{equation}

    WIP: Equilibrium solutions with stochasticity \& log/CRRA preferences
\end{frame}

%----------------
\section{Calibration}
\begin{frame}{Calibration (idea phase)}
    \begin{itemize}
        \item \textbf{Data sources:} Ethereum prices from Messari API, txn fees from Dune Analytics, staking data from beaconcha.in
        \item \textbf{Period:} Sep 2022 - now, down to block frequency (12s) 24/7
        \item Proxy for transactional benefits/convenience yields: average onchain txn processing per second $a_t$\citep{cong2022staking}
        \begin{itemize}
            \item other potential proxies: Metcalfe's measure $\log(DailyActiveAddresses^2)$; \href{https://www.ncsl.org/financial-services/cryptocurrency-2023-legislation}{index on US crypto regulation (NCSL.org)}
        \end{itemize}

        \item Proxy for hacking: manually index major hacks and wallet losses
    \end{itemize}
\end{frame}

@@

% -----------------
\section*{}
\begin{frame}[allowframebreaks, noframenumbering]{References}
    %\nocite{*}
    %\bibliographystyle{apalike}
    %\bibliography{references}
    \printbibliography
\end{frame}
